On the use of decision trees to identify the local extrema in parallel global optimization algorithms

### 2023-02-01 2023/PAVT/ParallelDecisionTree.tex
minor corrections

The investigating search is performed as follows. 
\begin{enumerate} 
\item	The step value is determined (it is different for each coordinate and can be varied in the course  of search).  
\item	The search step is considered to be successful if the value of the objective function at the check  point doesn't exceed the value of the objective function at the initial point.  
\item	Otherwise, it is necessary to return to the previous item and make a step in the reverse direction.  
\item	After making the steps in all $N$ coordinates, the investigating search is completed. The point  obtained is called the base point. 
\end{enumerate}

@@

\begin{figure}[!h] 
	\begin{center} 
		\begin{minipage}[h]{0.8\linewidth} 
			\includegraphics[width=1\linewidth]{figure/fig1.pdf} 
			\caption{An example of iterations of the Hooke-Jeeves algorithm} %%  подпись к рисунку 
			\label{fig:fig1} 
		\end{minipage} 
	\end{center} 
\end{figure}

@@

The decision tree is a tool used for an automated analysis of big data arrays, which is applied in the  machine learning. Decision tree is a binary tree (a tree, in which each non-leaf node has two child nodes). It can be used for solving the classification problems as well as the regression ones. When solving  the classification problems, each leaf of the tree is marked by a class label, and several leafs can have  the same labels. In the case of constructing a regression, a constant is assigned to each leaf of the tree.   Therefore, the approximating function obtained is a piecewise-constant one. In our case, the decision tree constructs the function $\psi(y)$ as a piecewise-constant  approximation of $\varphi(y)$ in the search domain. Let us denote the value  computed by the  decision tree at the point $y$ as $z' = \psi(y)$.

@@

Fig. \ref{fig:fig2} presents a contour plot of an objective function and the trial points; Fig.  \ref{fig:fig2_2} presents corresponding decision tree.

\begin{figure}[ht!]
	\begin{center}
		\begin{minipage}[h]{0.9\linewidth}
			\includegraphics[width=1\linewidth]{figure/fig4.png}
			\caption{A function from the GKLS generator before using Peano curves} %% подпись к рисунку
			\label{fig:fig2}
		\end{minipage}
	\end{center}
\end{figure}

\begin{figure}[ht!]
	\begin{center}
		\begin{minipage}[h]{0.9\linewidth}
			\includegraphics[width=1\linewidth]{figure/fig5.png}
			\caption{A figure with a two-dimensional decision tree} %% подпись к рисунку
			\label{fig:fig2_2}
		\end{minipage}
	\end{center}
\end{figure}

>>>>

\begin{figure} 
	\begin{center} 
		\begin{minipage}[h]{0.8\linewidth} 
			\includegraphics[width=1\linewidth]{figure/fig1.pdf} 
			\caption{An example of iterations of the Hooke-Jeeves algorithm} %%  подпись к рисунку 
			\label{fig:fig1} 
		\end{minipage} 
	\end{center} 
\end{figure}

The investigating search is performed as follows (see Fig. \ref{fig:fig1}).
\begin{enumerate} 
\item	The step value is determined (it is different for each coordinate and can be varied in the course  of search).  
\item	The search step is considered to be successful if the value of the objective function at the check  point doesn't exceed the value of the objective function at the initial point.  
\item	Otherwise, it is necessary to return to the previous item and make a step in the reverse direction.  
\item	After making the steps in all $N$ coordinates, the investigating search is completed. The point  obtained is called the base point. 
\end{enumerate}

@@

@@

The decision tree is a tool used for an automated analysis of big data arrays, which is applied in the  machine learning. Decision tree is a binary tree (a tree, in which each non-leaf node has two child nodes). It can be used for solving the classification problems as well as the regression ones. When solving  the classification problems, each leaf of the tree is marked by a class label, and several leafs can have  the same labels. In the case of constructing a regression, a constant is assigned to each leaf of the tree.   Therefore, the approximating function obtained is a piecewise-constant one. In our case, the decision tree constructs the function $\psi(y)$ as a piecewise-constant  approximation of $\varphi(y)$ in the search domain. Let us denote the value  computed by the  decision tree at the point $y$ as $z' = \psi(y)$.
Fig. \ref{fig:fig2} presents a graph of the objective function $\varphi(y)$; Fig. \ref{fig:fig2_2} presents corresponding approximation $\psi(y)$ built using decision tree.

\begin{figure}
	\begin{center}
		\begin{minipage}[h]{0.8\linewidth}
			\includegraphics[width=1\linewidth]{figure/fig5.png}
			\caption{An objective function $\varphi(y)$ from the test class} %% подпись к рисунку
			\label{fig:fig2}
		\end{minipage}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
		\begin{minipage}[h]{0.8\linewidth}
			\includegraphics[width=1\linewidth]{figure/fig4.png}
			\caption{A piecewise-constant  approximation $\psi(y)$ of the function $\varphi(y)$} %% подпись к рисунку
			\label{fig:fig2_2}
		\end{minipage}
	\end{center}
\end{figure}

@@
